% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textwidth}{5.1in} % set width of text portion
\usepackage{wasysym}
\usepackage{amssymb}

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Syed Muhammad Qasim Sarfraz}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{syed.qasim.sarfraz@gmail.com}

\moveleft.5\hoffset\centerline{+4915204902253}

\begin{resume}

\section{Career Summary} Software Engineer with a passionate and a self driven personality with experience in software development and system engineering of cloud native softwares.

\section{Computer \\ Skills} {\sl Languages \& Software:} Golang, Python, Ansible, Bash, Git, Jenkins, Docker, Kubernetes, AWS and VSphere.\\
                {\sl Operating Systems:} Linux

\section{Work \\ Experience}
\textbf{DevOps/Full Stack Engineer} at Zeal Network SE, Hamburg \hfill     Noc 2017-June 2022 \\
- Part of a development team with keys roles including:
    \begin{itemize}
      \item Planning and migrating on-premises platform to a cloud provider. \textit{(Kubernetes, Kubespray, Cilium and AWS)}
      \item Developing and maintaining product \textbf{micro-services} with cloud native approach. \textit{(Golang and Kubernetes)}
      \item Building \textbf{reliable systems} by running Kubernetes based platform in production on multiple cloud providers with centralized logging, monitoring and alerting solutions. \textit{(Ansible, Docker, Kubernetes and VSphere/AWS)}
    \end{itemize}    \\ \\
\textbf{DevOps Engineer} at INTECH Process Automation, Lahore \hfill     Mar 2017- Oct 2017 \\
- Responsible for deployment, maintenance, scalability and system engineering of advanced data and software solutions for IoT platform. \textit{(Ansible and DC/OS)}   \\ \\
{\bf Design Engineer III} at Xgrid, Islamabad\hfill     Oct 2014 - Feb 2017 \\
- Senior member of PLUMgrid Cloud Solutions team with responsibilities including design and development of automated deployments, upgrades and maintenance of PLUMgrid Products. The key projects completed here include:
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item \textbf{Design and development} for PLUMgrid Docker based installation. \textit{(Puppet, Ansible, Bash and Docker)}
        \item \textbf{Lead Developer} for PLUMgrid and Red Hat OpenStack solution for automated installations and upgrades. \textit{(Puppet, Ansible, Bash and LXC)}
        \item \textbf{Developer} for PLUMgrid Life Cycle Manager for robust automated production grade deployments. \textit{(Puppet and Bash)}
    \end{itemize}

\textbf{Site Experince} at PLUMgrid HQ, California \hfill     Jan-Mar 2016 \\
- 8 weeks training in PLUMgrid HQ, Santa Clara.   \\ \\

\section{Education} {\sl Bachelor of Science,} Electrical Engineering \hfill 2010-2014 \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                University of Engineering and Technology, Lahore \\
	             \textit{Concentration} : \textbf{Computers}

\section{Achievements \\ \& Participation} Speaker at Honeypot Tech Talk with titile, \textbf{Kubernetes - the eSailors way}. \\ \\
Contributor in \textbf{open source communities} e.g Kubespray, CoreDNS etc \\ \\
\textbf{PLUMgrid outstanding achievement} award.
\end{resume}
\end{document}
